Analytical reproducibility of published meta-analyses on clinical psychological

### 2022-09-05 manuscript.Rmd
Adding data

author:
 - name: "Rubén López-Nicolás"
   affiliation: "1"
   corresponding: yes
   adress: "Facultad de Psicología, Campus de Espinardo, Universidad de Murcia, edificio n° 31, 30100, Murcia, Spain"
   email: "rlopez@um.es"
 - name: "Daniel Lakens"
   affiliation: "2"
 - name: "Jose A. López-López"
   affiliation: "1"
 - name: "Maria Rubio-Aparicio"
   affiliation: "3"
 - name: "Carmen López-Ibáñez"
   affiliation: "1"
 - name: "Desirée Blázquez-Rincón"
   affiliation: "1"
 - name: "Alejandro Sandoval-Lentisco"
   affiliation: "1"
 - name: "Julio Sánchez-Meca"
   affiliation: "1"

>>>>

author:
 - name: "Rubén López-Nicolás"
   affiliation: "1"
   corresponding: yes
   adress: "Facultad de Psicología, Campus de Espinardo, Universidad de Murcia, edificio n° 31, 30100, Murcia, Spain"
   email: "rlopez@um.es"
 - name: "Daniel Lakens"
   affiliation: "2"
 - name: "Jose A. López-López"
   affiliation: "1"
 - name: "Alejandro Sandoval-Lentisco"
   affiliation: "1"
 - name: "Maria Rubio-Aparicio"
   affiliation: "3"
 - name: "Carmen López-Ibáñez"
   affiliation: "1"
 - name: "Desirée Blázquez-Rincón"
   affiliation: "1"
 - name: "Julio Sánchez-Meca"
   affiliation: "1"
